\textsf{Are large language models superhuman chemists?}

### 2024-03-31 src/tex/sections/manually_sources_table.tex
[showyourwork]

    \toprule
    source & description & question count \\
    \midrule
NMR spectroscopy & Questions are based on images shared via the Twitter account \href{https://twitter.com/NMRspectroscopy}{NMRspectroscopy} && \variable{output/question_count_per_dir/json_file_counts_nmr.txt} \\
\midrule
Analytical chemistry & Questions are based on exercises in master student examination at the FSU Jena, Germany &&  \variable{output/question_count_per_dir/json_file_counts_analytical_chemistry.txt} \\
\midrule
\multirow{2}{*}{General chemistry} & Questions originate from examinations for grade 10 at the Marist Comprenhensive Academy Uturu, Nigeria && \variable{output/question_count_per_dir/json_file_counts_Gen_Chem_MCA.txt} \\
 & Questions originate from the Bachelor of Science (for chemistry) courses at the TUM, Germany && \variable{output/question_count_per_dir/json_file_counts_ac_faessler_tum.txt} + \variable{output/question_count_per_dir/json_file_counts_pum_tum.txt} \\
 \midrule
Functional materials and  nanomaterials & Questions are based on exercises in a seminar conducted at the FSU Jena, Germany && \variable{output/question_count_per_dir/json_file_counts_func_mats_and_nanomats.txt} \\
\midrule
Combustion engineering & Based on a Master of Science examination paper at the University of Magdeburg, Germany && \variable{output/question_count_per_dir/json_file_counts_combustion_engineering.txt} \\
\midrule
Materials' synthesis & Questions are based on seminars on material synthesis from FSU Jena, Germany && \variable{output/question_count_per_dir/json_file_counts_materials_synthesis.txt} \\
\midrule
Chemistry olympiad & National and International Olympiads held in US, UK and Moldova && \variable{output/question_count_per_dir/json_file_counts_icho.txt} \\
\midrule
Organic reactivity & Based on exams in the Bachelor of Science in Chemistry at the TUM, Germany && \variable{output/question_count_per_dir/json_file_counts_organic_reactivity.txt} \\
\midrule
Periodic table & Manually created && \variable{output/question_count_per_dir/json_file_counts_periodic_table_properties.txt} \\
\midrule
Polymer chemistry & Based on examinations at the University of Hamburg, Germany && \variable{output/question_count_per_dir/json_file_counts_polymer_chemistry.txt} \\
\midrule
Textbook questions & Various textbooks covering biomolecular science, drug synthesis, molecular structure, organic chemistry, and X-ray crystallography && \variable{output/question_count_per_dir/json_file_counts_oup.txt} \\
\midrule
Safety & Based on the question bank published by the Federal/State Working Group  on Chemical Safety (BLAC), which is used for the expertise examination (“Sachkundepr\"ufung”) && \variable{output/question_count_per_dir/json_file_counts_blac_gfk.txt} \\
       & Based on toxicology exams at the LMU Munich, Germany && \variable{output/question_count_per_dir/json_file_counts_LMU_tox.txt} \\
       & Based on toxicology exams at the University of Vienna, Austria && \variable{output/question_count_per_dir/json_file_counts_tox_pharma_vienna.txt} \\
       & Based on toxicology exams at WWU Munster, Germany && \variable{output/question_count_per_dir/json_file_counts_tox_wwu.txt} \\
       & Based on exercises for lectures in high-energy density materials at LMU Munich, Germany && \variable{output/question_count_per_dir/json_file_counts_hedm_munich.txt} \\
       & Based on pharmacology exams at the University of Vienna, Austria && \variable{output/question_count_per_dir/json_file_counts_pharmacology_vienna.txt} \\
\bottomrule
\end{xltabular}

>>>>

    \toprule
    source & description & question count \\
    \midrule
NMR spectroscopy & Questions are based on images shared via the Twitter account \href{https://twitter.com/NMRspectroscopy}{NMRspectroscopy} && \variable{output/question_count_per_dir/json_file_counts_nmr.txt} \\
\midrule
Analytical chemistry & Questions are based on exercises in master student examination at the FSU Jena, Germany &&  \variable{output/question_count_per_dir/json_file_counts_analytical_chemistry.txt} \\
\midrule
\multirow{2}{*}{General chemistry} & Questions originate from examinations for grade 10 at the Marist Comprenhensive Academy Uturu, Nigeria && \variable{output/question_count_per_dir/json_file_counts_Gen_Chem_MCA.txt} \\
 & Questions originate from the Bachelor of Science (for chemistry) courses at the TUM, Germany && \variable{output/question_count_per_dir/json_file_counts_ac_faessler_tum.txt} + \variable{output/question_count_per_dir/json_file_counts_pum_tum.txt} \\
 \midrule
Functional materials and  nanomaterials & Questions are based on exercises in a seminar conducted at the FSU Jena, Germany && \variable{output/question_count_per_dir/json_file_counts_func_mats_and_nanomats.txt} \\
\midrule
Combustion engineering & Based on a Master of Science examination paper at the University of Magdeburg, Germany && \variable{output/question_count_per_dir/json_file_counts_combustion_engineering.txt} \\
\midrule
Materials' synthesis & Questions are based on seminars on material synthesis from FSU Jena, Germany && \variable{output/question_count_per_dir/json_file_counts_materials_synthesis.txt} \\
\midrule
Chemistry olympiad & National and International Olympiads held in US, UK and Moldova && \variable{output/question_count_per_dir/json_file_counts_icho.txt} \\
\midrule
Organic reactivity & Based on exams in the Bachelor of Science in Chemistry at the TUM, Germany && \variable{output/question_count_per_dir/json_file_counts_organic_reactivity.txt} \\
\midrule
Periodic table & Manually created && \variable{output/question_count_per_dir/json_file_counts_periodic_table_properties.txt} \\
\midrule
Polymer chemistry & Based on examinations at the University of Hamburg, Germany && \variable{output/question_count_per_dir/json_file_counts_polymer_chemistry.txt} \\
\midrule
Textbook questions & Various textbooks covering biomolecular science, drug synthesis, molecular structure, organic chemistry, and X-ray crystallography && \variable{output/question_count_per_dir/json_file_counts_oup.txt} \\
\midrule
Safety & Based on the question bank published by the Federal/State Working Group  on Chemical Safety (BLAC), which is used for the expertise examination (“Sachkundepr\"ufung”) && \variable{output/question_count_per_dir/json_file_counts_blac_gfk.txt} \\
       & Based on toxicology exams at the LMU Munich, Germany && \variable{output/question_count_per_dir/json_file_counts_LMU_tox.txt} \\
       & Based on toxicology exams at the University of Vienna, Austria && \variable{output/question_count_per_dir/json_file_counts_tox_pharma_vienna.txt} \\
       & Based on toxicology exams at WWU Munster, Germany && \variable{output/question_count_per_dir/json_file_counts_tox_wwu.txt} \\
       & Based on exercises for lectures in high-energy density materials at LMU Munich, Germany && \variable{output/question_count_per_dir/json_file_counts_hedm_munich.txt} \\
       & Based on pharmacology exams at the University of Vienna, Austria && \variable{output/question_count_per_dir/json_file_counts_pharmacology_vienna.txt} \\
       & Lab safety quizzes based on various sources && \variable{output/question_count_per_dir/json_file_counts_sci_lab_safety_test.txt} + \variable{output/question_count_per_dir/json_file_counts_lab_safety.txt} + \variable{output/question_count_per_dir/json_file_counts_stolaf.txt} + \variable{output/question_count_per_dir/json_file_counts_chemical_safety_mcq_exam.txt} + \variable{output/question_count_per_dir/json_file_counts_anderson.txt}\\
\bottomrule
\end{xltabular}
